STAT 450 Project: Real Estate

### 2020-03-20 src/2nd_draft.Rmd
formatting and eda updated

## R Markdown
libraries
```{r, message=F, warning=F}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)
library(broom)
library(glmnet)
library(dummies)
```

@@

```{r, warning=F, message=F, echo=FALSE}
## data setup
## Aggregated Data
assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))[,-1]
assessment_2020 <- read.csv(here("data","assessment_2020.csv"))[,-1]
# assessment_2020.full <- read_excel(here("data/Assessment", "2020 Only.xlsx"))
```

@@

**Table 1: Kruskal-Wallis Test of Mill Rate across Municipality and Tax Class**

@@

\pagebreak
###Linear Model

@@

For a dtailed look of how the models were fitted and evaluated, please refer to the **Appendix**.

```{r, warning=FALSE, echo=FALSE}
## model fitting
set.seed(123)
lambdas <- 10^seq(2, -3, by = -.1)
dummy_municipal<-dummy(assessment_transform$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_transform$TaxClassCode)

@@

for (i in 1:N) {
  ii <- sample(ii)
  pr1.n<-pr1.la <- pr1.f <- pr1.ri <- pr1.reduced <- rep(0, n)
  pr.n<-pr.la <- pr.f <- pr.ri <- pr.reduced <- rep(0, n)
  for (j in 1:k) {
    # ~ models trained!
    tmp.ri <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 0, family = "gaussian")
    tmp.la <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 1, family = "gaussian")
    tmp.reduced <- lm(rate ~ factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc)+AvgTotalAssessmentValue, 
                      data = x.data.frame[ii != j, ])
    tmp.full <- lm(rate ~ factor(AddressAssessorMunicipalityDesc)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount, 
                   data = x.data.frame[ii != j, ])
    tmp.n <- lm(rate ~ 1, 
                      data = x.data.frame[ii != j, ])

@@

boxplot(mspe1.la, 
        mspe1.ri, 
        mspe1.reduced, 
        mspe1.f, 
        mspe1.n,
        names = c("LASSO", 
                  "Ridge",
                  "Transformed", 
                  "Full",
                  "Null"
                  ), 
        col = c("steelblue","gray80",
                "pink", 
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Goodness of Fit",
        ylab = expression(hat(MSE)))

boxplot(mspe.la, 
        mspe.ri,
        mspe.reduced, 
        mspe.f, 
       mspe.n,
        names = c("LASSO", 
                  "Ridge", 
                  "Transformed", 
                  "Full",
                  "Null"
                  ), 
        col = c("steelblue","gray80", 
                "pink",
                "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Prediction Power",
        ylab = expression(hat(MSPE)))
```

@@

## Fit and get PMSE
assessment_2020.agg <- assessment_2020%>%
  mutate(AvgTotalAssessmentValue = assessTotal/propertyCount)%>%
  mutate(predict_rate = predict(linear_1,newdata = .))
resid<-assessment_2020.agg$predict_rate - assessment_2020.agg$rate
sqrt(sum(resid^2)/nrow(assessment_2020.agg))

# ## Final result
# municipality.list = c(
#   "Burnaby", 
#   "Coquitlam", 
#   "Delta", 
#   "Langley - City", 
#   "Langley - Township",
#   "Maple Ridge",
#   "Maple Ridge Rural", 
#   "North Vancouver - City",
#   "North Vancouver - Dist",
#   "Pitt Meadows", 
#   "Port Coquitlam", 
#   "Port Moody", 
#   "Richmond", 
#   "Surrey", 
#   "Vancouver", 
#   "White Rock", 
#   "West Vancouver", 
#   "Bowen Island", 
#   "Anmore", 
#   "Belcarra",
#   "Lions Bay",
#   "New Westminster")
# 
# ## Raw Data
# a <- assessment_2020.full%>%
#   filter(TaxClassCode %in% c("01","05","06"),
#          AddressAssessorMunicipalityDesc %in% municipality.list)

@@

# assessment_2020.final<- merge(a, b, by =c("AddressAssessorMunicipalityDesc", "TaxClassCode"), all.x = TRUE)

# write.csv(assessment_2020.final, "../Data/Assessment/assessment_2020.final")
write.csv(b, "../Data/assessment_2020_fit.csv")
```

@@

\pagebreak
## References

Links to source of data:

- Schedule 706 (https://www2.gov.bc.ca/gov/content/governments/local-governments/facts-framework/statistics/statistics)

@@

**Table 3: Data with missing mill rate**

@@

>>>>

```{r, message=F, warning=F, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)
library(broom)
library(glmnet)
library(dummies)
set.seed(123)
```

@@

```{r, warning=F, message=F, echo=FALSE}
## data setup
## Aggregated Data
assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))[,-1]
assessment_2020 <- read.csv(here("data","assessment_2020.csv"))[,-1]
```

@@

        Table 1: Kruskal-Wallis Test of Mill Rate across Municipality and Tax Class

@@

###Linear Model

@@

The distributions of goodness of fit and prediction power across models are displyed in Figure 7 and Figure 8, respectively, the distribution of null model is removed since it has larger values compared to all other models.

The distributions of MSPE across models are also displayed in Table 2.

```{r, warning=FALSE, echo=FALSE}
## model fitting
lambdas <- 10^seq(2, -3, by = -.1)
dummy_municipal<-dummy(assessment_transform$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_transform$TaxClassCode)

@@

for (i in 1:N) {
  ii <- sample(ii)
  pr1.n<-pr1.la <- pr1.f <- pr1.ri <- pr1.reduced <- rep(0, n)
  pr.n<-pr.la <- pr.f <- pr.ri <- pr.reduced <- rep(0, n)
  for (j in 1:k) {
    # ~ models trained!
    tmp.ri <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 0, family = "gaussian")
    tmp.la <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 1, family = "gaussian")
    tmp.reduced <- lm(rate ~ factor(TaxClassCode)+
                        factor(AddressAssessorMunicipalityDesc)+
                        AvgTotalAssessmentValue, 
                      data = x.data.frame[ii != j, ])
    tmp.full <- lm(rate ~ factor(AddressAssessorMunicipalityDesc)+
                     factor(TaxClassCode)+
                     assessTotal+
                     landTotal+
                     improvementTotal+
                     propertyCount, 
                   data = x.data.frame[ii != j, ])
    tmp.n <- lm(rate ~ 1, 
                      data = x.data.frame[ii != j, ])

@@

boxplot(mspe1.la, 
        mspe1.ri, 
        mspe1.reduced, 
        mspe1.f, 
        names = c("LASSO", 
                  "Ridge",
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80",
                "pink", 
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = " Figure 7: Goodness of Fit",
        ylab = expression(hat(MSE)))

boxplot(mspe.la, 
        mspe.ri,
        mspe.reduced, 
        mspe.f,
        names = c("LASSO", 
                  "Ridge", 
                  "Transformed", 
                  "Full"
                  ), 
        col = c("steelblue","gray80", 
                "pink",
                "tomato"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2,
        main = "Figure 8: Prediction Power",
        ylab = expression(hat(MSPE)))
```

                Table 2: Prediction Power of All Models

Model | PMSE:Min | PMSE:Mean | PMSE:Max
-----|-----|-----|-----|
Full Model | 6.50 | 6.97 | 7.59 |
Transformed Model | 5.60 | 5.92 | 6.51 |
Null Model | 36.67 | 36.87 | 37.26 |
The Lasso for Full Model | 5.58 | 5.91 | 6.40 |
Ridge Regression for Full Model | 5.53 | 5.88 | 6.39 |

For a detailed look of how the models were fitted and evaluated, please refer to the **Appendix**.

@@

## Fit and get PMSE
assessment_2020.agg <- assessment_2020%>%
  mutate(AvgTotalAssessmentValue = assessTotal/propertyCount)%>%
  mutate(predict_rate = predict(linear_1,newdata = .))
resid<-assessment_2020.agg$predict_rate - assessment_2020.agg$rate
#sqrt(sum(resid^2)/nrow(assessment_2020.agg))

@@

write.csv(b, "../Data/assessment_2020_fit.csv")
```

@@

@@

                    Table 3: Data with missing mill rate

@@

## References
